Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-26 writeup/parkinsons.tex
rerun biclustering plots
update ap statistics to match rerun
rerun plots, data for hc

\subsection{Cutting Trees}
\begin{table}[h]
  \centering
  \begin{tabular}{l|l|l|l}
    Method & Condition & n & Figure \\
    \hline
    Complete & $k = 4$ & 4 (665/74/35/7) & ~\ref{fig:hc-summaries-complete-k4} \\
    Complete & \texttt{dynamicTreeCut}\tablefootnote{Package \texttt{dynamicTreeCut} in R (Langfelder P,
  Zhang B, Horvath S (2007)). Hybrid method, minimum cluster selection
parameters} & 11 (7/270/138/83/79/49/46/39/35/35) &
    ~\ref{fig:hc-summaries-complete-dynamic} \\
    Ward & $k = 4$ & 4 (294/236/120/131) & ~\ref{fig:hc-summaries-ward-D-k4} \\
    Ward & $h = 60$ & 6 (97/236/120/197/91/40) &
    ~\ref{fig:hc-summaries-ward-D-h60} \\
  \end{tabular}
  \caption{Clusters from Tree Cutting}
  \label{tab:tree-cutting}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hc-summaries-ward-D-h60.pdf}
  \caption{Using Ward (1963) dissimilarity, cutting tree at $h = 60$}
  \label{fig:hc-summaries-ward-D-h60}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|l}
  Cluster & Size \\
  \hline
  1 & 54 \\
  2 & 68 \\
  3 & 25 \\
  4 & 259 \\
  5 & 102 \\
  6 & 68 \\
  7 & 185 \\
  8 & 20 \\
  \end{tabular}
  \caption{AP Cluster Sizes}
  \label{tab:ap-cluster-sizes}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}

>>>>

\subsection{Cutting Trees}
\begin{table}[h]
  \centering
  \begin{tabular}{l|l|l|l}
    Method & Condition & n & Figure \\
    \hline
    Complete & $k = 4$ & 4 (790/81/18/12) & ~\ref{fig:hc-summaries-complete-k4} \\
    Complete & \texttt{dynamicTreeCut}\tablefootnote{Package \texttt{dynamicTreeCut} in R (Langfelder P,
  Zhang B, Horvath S (2007)). Hybrid method, minimum cluster selection
parameters} & 13 (255/99/77/64/62/58/56/46/44/41/37/32/30) &
    ~\ref{fig:hc-summaries-complete-dynamic} \\
    Ward & $k = 4$ & 4 (200/237/263/201) & ~\ref{fig:hc-summaries-ward-D-k4} \\
    Ward & $h = 100$ & 3 (437/263/201) &
    ~\ref{fig:hc-summaries-ward-D-h100} \\
  \end{tabular}
  \caption{Clusters from Tree Cutting}
  \label{tab:tree-cutting}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hc-summaries-ward-D-h100.pdf}
  \caption{Using Ward (1963) dissimilarity, cutting tree at $h = 100$}
  \label{fig:hc-summaries-ward-D-h100}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|l}
  Cluster & Size \\
  \hline
  1 & 63 \\
  2 & 53 \\
  3 & 85 \\
  4 & 122 \\
  5 & 48 \\
  6 & 126 \\
  7 & 123 \\
  8 & 102 \\
  9 & 166 \\
  10 & 13 \\
  \end{tabular}
  \caption{AP Cluster Sizes}
  \label{tab:ap-cluster-sizes}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{biclust-bubbleplot-16.pdf}
  \caption{Bubbleplot $N = 16$}
  \label{fig:bubbleplot-16}
\end{figure}
